### 2019-08-19 maciek.tex
Some fixes

\begin{theorem}
  The rebalancing cost for the greedy algorithm is $O(k)$.
  \maciek{Greedy = find the cheapest feasible partition}
  \label{rebalancing-cost}
\end{theorem}

@@

\begin{proof}
  The adversary issues at most $3\ell$ requests, as otherwise the perfect partition would not exist. Each request issues at most one rebalancing, and by Theorem~\ref{rebalancing-cost}, the total cost of any algorithm is $O(k\cdot \ell)$.
\end{proof}

>>>>

\begin{theorem}
  The rebalancing cost for the greedy algorithm for $k=3$ is $O(1)$.
  \maciek{Greedy = find the cheapest feasible partition}
  \label{rebalancing-cost}
\end{theorem}

@@

\begin{proof}
  The adversary issues at most $3\ell$ requests, as otherwise the perfect partition would not exist. Each request issues at most one rebalancingfor the greedy algorithm, and by Theorem~\ref{rebalancing-cost}, the total cost of any algorithm is $O(k\cdot \ell)$.
\end{proof}
